---
title: "Sample RMarkdown"
author: "Shanthal"
date: "`r Sys.Date()`"
output: html_document
---
# Introduction

This report provides an overview of students in different courses and their year levels, including their number of absences.

## Data

We have a dataset that contains information about students, including their names, courses, year levels, and number of absences. Below loads the data of the first few records.

```{r}
# Sample data
students <- data.frame(
  Name = c("Alice", "Bob", "Charlie", "David", "Eve"),
  Course = c("BSIT", "BSCS", "BSIT", "BMMA", "BSCS"),
  Year_Level = c(2, 3, 1, 4, 2),
  Absences = c(3, 2, 5, 1, 4)
)

# Show the first few records
head(students)
```

## Graph View

This shows a graph view of the student data, including their number of absences.
```{r}
# Load the necessary packages
library(ggplot2)

# Create a bar graph showing the number of absences
ggplot(students, aes(x = Name, y = Absences, fill = Course)) +
  geom_bar(stat = "identity") +
  labs(title = "Number of Absences by Student and Course", x = "Student Name", y = "Number of Absences") +
  scale_fill_brewer(palette = "Set1") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### This is an h3 tag

I added a new column named *"Absences"* to the student data frame and included it in the data display. You can now see the number of absences for each student in the report. <http://rmarkdown.rstudio.com>


